%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

\cvsubsection{Peer-reviewed articles}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {[8] Higino, G.T., \textbf{Banville, F.}, Dansereau, G., Forero-Muñoz, N.R., Windsor, F., and Poisot, T. (2023). Mismatch between IUCN range maps and species interactions data illustrated using the Serengeti food web. PeerJ, 11, e14620. https://doi.org/10.7717/peerj.14620} % Citation
    {} {} {2023} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[7] Lawlor, J., \textbf{Banville, F.}, Forero-Muñoz, N.R., Hébert, K., Martínez-Lanfranco, J.A., Rogy, P., and MacDonald, A.A.M. (2022). Ten simple rules for teaching yourself R. PLOS Computational Biology, 18(9), e1010372. https://doi.org/10.1371/journal.pcbi.1010372} % Citation
    {} {} {2022} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {[6] Strydom, T., Bouskila, S., \textbf{Banville, F.}, Barros, C., Caron, D., Farrell, M.J., Fortin, M.-J., Hemming, V., Mercier, B., Pollock, L.J., Runghen, R., Dalla Riva, G.V., and Poisot, T. (2022). Food web reconstruction through phylogenetic transfer of low-rank network representation. Methods in Ecology and Evolution, 13(12), 2838‑2849. https://doi.org/10.1111/2041-210X.13835} % Citation
    {} {} {2022} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {[5] Strydom, T., Catchen, M.D., \textbf{Banville, F.}, Caron, D., Dansereau, G., Desjardins-Proulx, P., Forero-Muñoz, N.R., Higino, G., Mercier, B., Gonzalez, A., Gravel, D., Pollock, L., and Poisot, T. (2021). A roadmap towards predicting species interaction networks (across space and time). Philosophical Transactions of the Royal Society B: Biological Sciences, 376(1837), 20210063. https://doi.org/10.1098/rstb.2021.0063} % Citation
    {} {} {2021} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {[4] Higino G., Forero-Muñoz, N.R., \textbf{Banville, F.}, Dansereau, G., and Poisot, T. (2021). Computers can help us find raccoons and other living creatures. Front. Young Minds. 9(595275). https://doi.org/10.3389/frym.2021.595275} % Citation
    {} {} {2021} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[3] \textbf{Banville, F.}, Vissault, S., and Poisot, T. (2021). Mangal.jl and EcologicalNetworks.jl: Two complementary packages for analyzing ecological networks in Julia. Journal of Open Source Software, 6(61), 2721. https://doi.org/10.21105/joss.02721} % Citation
    {} {} {2021} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[2] Dansereau, G., \textbf{Banville, F.}, Basque, E., MacDonald, A.A.M., and Poisot, T. (2020). [Re] Chaos in a three-species food chain. ReScience C, 6(3), 5. https://doi.org/10.5281/zenodo.4022518} % Citation
    {} {} {2020} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[1] MacDonald, A.A.M., \textbf{Banville, F.}, and Poisot, T. (2020). Revisiting the links-species scaling relationship in food webs. Patterns, 0(0). https://doi.org/10.1016/j.patter.2020.100079} % Citation
    {} {} {2020} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

\cvsubsection{Preprints}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {[2] \textbf{Banville, F.}, Gravel, D., and Poisot, T. (2023). What constrains food webs? A maximum entropy framework for predicting their structure with minimal biases. arXiv (arXiv:2210.03190). https://doi.org/10.48550/arXiv.2210.03190} % Citation
    {} {} {2023} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[1] Strydom, T., Bouskila, S., \textbf{Banville, F.}, Barros, C., Caron, D., Farrell, M.J., Fortin, M.-J., Hemming, V., Mercier, B., Pollock, L.J., Runghen, R., Dalla Riva, G.V., and Poisot. T.  (2022). Graph embedding and transfer learning can help predict potential species interaction networks despite data limitations. EcoEvoRxiv. https://doi.org/10.32942/osf.io/vyzgr} % Citation
    {} {} {2022} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}

