%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}

\cvsubsection{Organized sessions}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {[2] Leroux, E., Mélançon, V., \textbf{Banville, F.}, Brémaud, J., Robitaille, F., and Gholamhosseini, M. (2023, March 16-17). Complexity matters: subjectivity as practice in contemporary biology [Conference]. 33rd Biology Symposium of the University of Montreal, Montreal, Qc, Canada.} 
    {} {} {2023} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[1] Dansereau, G., \textbf{Banville, F.}, and Strydom, T. (2022, August 14-19). Space Oddity: Thinking about ecological networks across space [Inspire session]. ESA and CSEE Joint Meeting, Montreal, Qc, Canada.} 
    {} {} {2022} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
 
\cvsubsection{Contributed talks}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {[6] \textbf{Banville, F.}, Gravel, D., and Poisot, T. (2023, May 8-12). Comment les réseaux de prédateurs et de proies sont-ils structurés dans les milieux naturels? [Conference presentation]. 90e congrès de l’ACFAS, Montreal, Qc, Canada.} 
    {} {} {2023} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[5] \textbf{Banville, F.}, Gravel, D., and Poisot, T. (2022, August 14-19). What constrains food webs? A maximum entropy model for predicting their structure with minimal biases [Conference presentation]. 2022 Annual Meeting of the Ecological Society of America (ESA), Montreal, Qc, Canada.}
    {} {} {2022} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[4] \textbf{Banville, F.}, Gravel, D., and Poisot, T. (2022, March 25). Food webs of maximum entropy: A story of ecology and stochasticity [Conference presentation]. 32nd Biology Symposium of the University of Montreal, Montreal, Qc, Canada.} 
    {} {} {2022} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[3] \textbf{Banville, F.}, Gravel, D., and Poisot, T. (2020, October 22). Predicting networks of species interactions [Conference presentation]. IVADO Digital October 2020, virtual.}
    {} {} {2020} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[2] \textbf{Banville, F.}, MacDonald, A.A.M., Gravel, D., and Poisot, T. (2020, February 19). How to estimate network structure without interaction data [Conference presentation]. Extreme Climate Events Symposium 2020, Toronto, On, Canada.}
    {} {} {2020} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[1] \textbf{Banville, F.}, MacDonald, A.A.M., Gravel, D., and Poisot, T. (2019, December 18-20). How to estimate network structure without data [Conference presentation]. 10th Annual QCBS Symposium, Montreal, Qc, Canada.}
    {} {} {2019} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

\cvsubsection{Lightning talks}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {[4] \textbf{Banville, F.}, Gravel, D., and Poisot, T. (2022, March 29). Interactions entre espèces : une histoire d’écologie et de hasard [Conference short presentation]. My IVADO research project in 180 seconds, Montreal, Qc, Canada.}
    {} {} {2022} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[3] \textbf{Banville, F.}, Gravel, D., and Poisot, T. (2021, October 28). Predicting food webs across space: First estimates of food-web structure derived from species richness [Conference short presentation]. IVADO Digital October 2021, virtual.}
    {} {} {2021} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[2] \textbf{Banville, F.}, Gravel, D. and Poisot, T. (2020, December 14-16). Trophic-METE: A parsimonious theory of food-web structure [Conference short presentation]. 11th Annual QCBS Symposium, virtual.}
    {} {} {2020} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[1] \textbf{Banville, F.}, Vissault, S., Bélisle, Z., Hoebeke, L., Stock, M., Szefer, P., and Poisot, T. (2020, July 29-31). Analyzing species interaction networks in Julia [Conference short presentation]. Juliacon 2020, virtual.}
    {} {} {2020} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}


\cvsubsection{Posters}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {[2] \textbf{Banville, F.}, Gravel, D. and Poisot, T. (2021, December 8-10). Given limited knowledge, what can we say about a food web’s properties? [Poster presentation]. 12th Annual QCBS Symposium, virtual.}
    {} {} {2021} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {[1] \textbf{Banville, F.}, Gravel, D. and Poisot, T. (2020, December 14-16). Trophic-METE: A parsimonious theory of food-web structure [Poster presentation]. 11th Annual QCBS Symposium, virtual.}
    {} {} {2020} 
    {
      \begin{cvitems} % Description(s)
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

